Determinism, Complexity, and Predictability in Computer Performance

### 2014-03-05 related.tex
editing

\section{Related Work}

@@

Entropy though Generating partitions 
works **if** you have generating parition but not if you don't

>>>>

\section{Related Work {\color{red} NOT EDITABLE}}\label{sec:related}

@@

The ideal method of computing the entropy of a system is via \emph{generating partitions}~\cite{lind95}, a technique which partitions observations into symbols in a way which preserves the underlying dynamics. Unfortunately, outside of one-dimensional unimodal maps and a few select higher dimensional maps, generating partitions are highly non-trivial to compute and often have fractal boundaries~\cite{eisele1999}. Furthermore, the underlying dynamic needs to be known to construct the generating partition. Unfortunately, using any partition (such as those produced by simply binning the data) other than the generation partition induces spurious complexity to the resulting symbolic sequence, thus misrepresenting the entropy of the underlying system~\cite{bollt2001}.
